Benefits and risks associated with children’s and adolescents’ interactions with electronic screens: An umbrella review

### 2023-03-06 reports/revision_letter.Rmd
Address additional comments

```{r setup-chunk, include = FALSE}
targets::tar_load(c(manuscript, manuscript_md))
manuscript <- revise::read_manuscript("reports/manuscript.md", PDF = TRUE)
```

@@

# Editor Comments
```{asis}
Reviewer 3 points out that your last search date is May 2020. We agree that this means the review is not as timely as it could be and ask that you update your search to September 2022, and redo your analyses with all newly included studies.
```

@@

```{asis}
Reviewer 2's concerns about the appropriateness of your technical approach (notably: subjective characteristics of review selection, your statistical approach, and your choice to harmonize metrics of effect sizes) are significant and we ask that you prioritise addressing these issues when redoing your analyses.
```

@@

```{asis}
Both reviewers 2 and 3 are concerned about the lack of information on risk of bias assessment and population characteristics. Please ensure this information is clearly available and add data on both to Table 1.
```

```{asis}
Reviewer 1 highlights the inappropriateness of causal language given that the majority of included studies speak to association, not causation. Please remove all inappropriate use of causal language accordingly.
```

Please see response to Reviewer 1, \Comment{causal_lang}.

@@

```{asis}
As the authors note, “screen time” as a metric is highly criticized and problematic. This begs the question, though, of whether a wide-scale review of this sort, which retains a focus on screen time (although it also acknowledges other more nuanced metrics of exposure), is further perpetuating the issues seen by the broader field.
```

@@

`r revise::get_revision("r1_1")`

```{asis}
The authors note that “no review has synthesized the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviours, and wellbeing.” The authors end up concluding that there are different magnitude and directions of associations for different outcomes and exposures (and, indeed, the mechanisms of these are highly different depending on the predictor-outcome combination), which makes me wonder whether casting such a wide net is helping the reader understand more or less about the research to date on technology use and child/adolescent outcomes? I would want to hear more justification in the manuscript itself on why they assert it is helpful to try and paint them with one broad brush?
```
\WorkInProgress
\todo{Suggestions welcome here}

@@

`r revise::get_revision("r1_2")`

```{asis}
Page 10 notes that the study “examined the combinations of exposure and outcomes and removed any effects that appeared more than once, keeping the effect with the largest total sample size.” Did this take into consideration whether some meta-analyses of the same exposure-outcome pairs may have included mostly different studies (i.e., because they focused on different date ranges or some other inclusion criteria)?
```

@@

```{asis causal_lang}
Causal language- The present study sought to “provide a holistic perspective on the influence of screens on children's lives across a broad range of outcomes,” but I am not convinced that the studies included in the meta-analyses are designed in ways that allow us to understand causal IMPACT at all. Many have criticized this literature for being largely self-reported (with flaws inherent to this method, which are reviewed in the present manuscript's discussion), observational, and cross-sectional, with very few rigorous experimental or well-controlled longitudinal designs that would enable researchers or the public to draw robust conclusions about the direction of associations. I fear that this comprehensive review, though rigorous, does not adequately attend to the fact that we do not usually know whether screens are causing helps or harms for youth, if different types of youth behaviors may be causing them to engage more with screens (e.g., sedentary youth may seek out more screen time; depressed youth may turn more to social media as an avoidance strategy), or if indeed there are third variables driving observed associations. Although the review here does a great job of summarizing the direction and strengths of associations across studies, I fear that it does not attend to these important issues in terms of how one ought to interpret them.
```

@@

`r revise::get_revision("r1_4")`

@@

```{asis}
The manuscript notes that the nature of the data allowed for few age-based conclusions- I fear that this is a substantial limitation that deserves more discussion. It seems difficult to characterize all children's media use from age 0-18 in the same way, especially across such a wide range of developmental outcomes. A more nuanced treatment of developmental considerations would have been appreciated.
```

@@

```{asis}
I appreciate the opportunity to review this manuscript focusing on the impact of screen use on child well-being. This umbrella review organized findings from meta-analyses by child outcomes and screen types, converted pooled data into Pearson correlations as a unified estimate to facilitate cross-study comparisons, and reached a conclusion that general screen use and social media were associated with harmful impacts on child learning, literacy, body composition, and depression, and the potential risks could be mitigated by the content and context of screen use. This conclusion is somewhat similar to that of another umbrella review conducted by Stiglic and Viner in 2019 (PMID: 30606703). However, the current one made advances on including studies examining educational screen time and social media and harmonizing data from meta-analyses. 
```

@@

```{asis}
Abstract:

@@

```{asis}
Summary:
Page 4 line 59: the lack of comprehensive evidence hampers efforts to make an informed decision.
```

@@

```{asis}
Introduction:
Page 5 line 84-86: please further justify how a review study would make the limited evidence base less lacking or generate new findings.
```

@@

`r revise::get_revision("r1_2")`

```{asis}
Page 5 line 87-90: I suggest improving the logic flow and citing more recent studies (2016 or newer) to highlight the potentially new additions of the current review. 
```

@@

```{asis}
Page 5 line 91-94: Please provide a more in-depth explanation on the advantages of a review study to include a broad spectrum of health outcomes. 
```

@@

```{asis}
Page 6 line 96-104: these guidelines provide age-staged recommendations and mainly target on recreational screen time. New evidence to support or reject these recommendations are important breakthroughs. So how does the current review contribute to the refinement of these guidelines? It could be proposed here to strengthen the justification of this study, and also need to be addressed in the discussion section. 
```

@@

```{asis}
Page 6 line 104-107: this is not a direct contrast. Longer screen time is needed to pose mental health risks, but short screen time can lead to other health issues. While guidelines are built on a comprehensive examination of health outcomes. Thus, I consider here as a weak argument/transition. The organization of the introduction section need to be improved. 
```

@@

```{asis}
Page 6 line 117-119: Stiglic and Viner's umbrella review summarized evidence across a broad range of outcome domains. Please further justify the current study in addition to theirs.
```

@@

```{asis outcomes}
Page 7 line 122: please define “any plausible outcomes” to make the scope more scientifically sound and robust. In addition, the result section included findings of behavioral outcomes (physical activity and sleep duration) which I was not considered as academic, health, and social-psychological outcomes. Thus, it is better to be clear about the types of outcomes at the beginning of the manuscript. 
```

We did not *a-priori* choose which outcomes would be included.
Instead, we chose to summarise the literature on for any meta-analysis where screen exposure was the independent variable.
We have removed the word "plausible", as we agree that makes the sentence less clear and this phrasing is more aligned with the eligibility critiera.
Our intention in the introduction is not to preempt the results, which means we do not outline the outcomes found in the introduction.

```{asis}
Page 7 line 123: the authors stated the application of “a broad approach”, while highlighted the importance of nuanced findings and guidelines. The introduction section would be improved by balancing these two important aspects. 
```

@@

```{asis}
Methods:
Page 8 line 146-148: the effects of screen use on youth with a clinical condition are likely be different from those of the general population. If this review included any, the population characteristics should be specified in the result section or in the figures. 
```

@@

```{asis}
Page 8 line 152: please define outcomes.
```

Per /comment{outcomes} above, we did not pre-specify outcomes and feel it would be inappropriate to revise our inclusion criteria.

```{asis}
Page 10 line 181-187: these two sections could be combined. 
```

@@

```{asis}
Page 10 line 190: Table 1 does not contain RoB info. 
```

@@

```{asis}
Page 10 line 195-196: the description of data conversion is not transparent. Pearson's r assumes linear relationship. But associations between screen use and well-being are often non-monotonic (Twenge 2020, PMID: 32303719). In addition, meta-analyses reporting odd ratios defined exposure outcomes in various ways. For example, Zhang et. al. 2016 compared the obesity risk by the lowest and highest TV viewing time, whereas Poorolajal et. al. 2020 compared watching TV > 1-2h/d with an unclear group. Can the harmonization of OR into R guarantee that the two values are comparable? Therefore, further justification is needed. 
```

@@

```{asis}
Page 10 Line 201-206: The inclusion/exclusion criteria are here and there (page 10 line 197-198, page 11 line 221-222, etc.). Please provide specific and full criteria of effect size inclusion/exclusion in one section.

@@

`r revise::get_revision("r2_17")`

```{asis}
Page 11 line 222: Egger's test is not suitable for evaluating publication bias of ORs.
```

@@

```{asis}
Page 11 line 229-231: An effect with statistical credibility but showing P < .05 indicate no association of interest. 
```

@@

```{asis}
Page 12 line 232-233: “include systematic reviews without meta-analyses” conflicts “alongside the main meta-analytic findings”.
```

@@

```{asis}
Page 12 line 235: Harmonizing the metric of effect size does not guarantee the comparability of the strength of associations. Please fully justify the current practice with a thorough analysis of the pros and cons.
```

@@

```{asis}
Page 12 line 238-243: A significant P was not a criterion to consider studies as credible in other reviews. Not sure why it is a reason for altering the original plan. 
```

@@

```{asis}
Results
Page 12 line 247-248: please add a description that 66 studies contributed unique effect sizes to the current review. 
```

This information is available here (not that the updated search increased the number of reviews):

`r revise::get_revision("r2_23")`

```{asis}
Figure 1: 1) what's the difference between references and studies in this figure? For those seven entries categorized as “non-studies”, what are they? 2) “other(explain)” is not self-explanatory. 3) what's the difference between non-target samples and wrong population? In addition, the total number in this box is 1848. 4) “larger study available”: I'm not confident about using sample size as a sole criterium of selecting studies. 
```

@@

```{asis}
Page 12 line 249-256: 1) I suggest adding a summary table (counts and percentages) of the basic characteristics of the included references/studies which including year range of publication, types of study designs, sample age categories, outcome types, and exposure types, quality assessment scores, etc. 2) The current description is quite confusing to me, for example, what does “cases” mean? How did you calculate up 197 cases? What appeared twice or more times, the combination of exposure/outcome by age group? 3) table 1: I suggest adding data of the original effect sizes. 
```

@@

```{asis}
Page 26 line 260-268, Information on quality assessment was provided in a supplementary file, not table 1. Please revise. 
```

@@

```{asis}
Page 27 line 291: Please provide pre-determined criteria of the magnitude of effects with supporting references. 
```

@@

```{asis}
Page 28 line 299-304: 119-31-30-43 = 15, not 17. 
Three methodological issues needs to be clarified or justified. 
1. The selection of reviews to generate “unique” comparisons appeared to be subjective/unclear.
2. The statistical approach extensively reduced the evidence pool. For example, 46 unique effects on education outcomes was reduced to 12 and 119 unique effects on health outcomes was reduced to 17. 
3. Harmonizing the metrics of effect sizes into r may be invalid and placing the converted effect sizes in forest plot is somewhat deceiving. Because across-study comparisons are not guaranteed due to variations in study design, setups of exposure and outcome variables.
```

@@

```{asis}
Discussion
Page 31 line 362-368: I think these are important nuances. If the analytical plan was subjective altered in order to generate more consistent associations. Then, the practice can introduce selection bias. I suggest adding qualitative syntheses of those studies removed by not meeting the “statistical credibility” criteria. 
```

@@

```{asis}
Page 31 line 380-383: both guidelines mentioned recreational sedentary screen time. It is not in all instances. 
```

@@

```{asis}
Page 32 line 389-391: I assume that the data of primary studies was retrieved by the team whenever possible. But “failed to provide study-level data” make me wonder did not those reviews provide reference information of the included studies? 
```

```{asis}
Page 32 line 395: from my point of view, the evidence strength generated from data from ten loosely designed cross-sectional studies is weaker than 5 rigorously designed intervention studies or longitudinal studies. I wonder how the quality and quantity of studies were balanced in the current study.
```

@@

```{asis}
OVERALL IMPRESSION

@@

@@

```{asis}
MAJOR COMMENTS

```{asis}
Another main issue that I have with the article is that I feel that a better description of supplementary materials is needed. I have not been able to find a consistent description of the materials that can be found in them. Moreover, in the case of the CSV documents a variable dictionary would be most welcome. Somewhat relatedly, in line 190 (and 260) it says “see table 1”, so I was hoping to see some summary on the risk of bias evaluation in the table. I have not been able to find it there. In the Prisma checklist item 18 it says that risk of bias assessments can be found in OSF, but no mention of OSF is provided in the main text. After going through all the supplementary materials, I have been able to find the ratings in a file. My reading from all this is that the article has gone through several iterations and some systematizing and cleaning should be carried out to present in a more clear way the supplementary materials (an index of contents with a short description,
table and figure captions, variable dictionary…)
```

```{asis}
MINOR COMMENTS

@@

```{asis}
The paragraph on age within the eligibility criteria is unclear to me: “(i.e., the highest individual study from the meta-analysis had a mean age was < 18 years).”: is it a mean age below eighteen (hence, potentially including some adults), or is it the oldest participant being under 18 (more clear-cut, but on the other hand limiting the number of outcomes)?
```

```{asis}
“In this review we adopted a population-level perspective, meaning that we examined electronic media exposure that occurs during typical daily living activities (e.g., home, school-based electronic media exposure).”: I do not think this paragraph is fully clear. 
```

```{asis}
“Outcomes: We included all reported outcomes.”: it might be worth adding “on benefits and risks”
Lines 200-204: it is unclear to me whether this refers to effects found within the same meta-analysis, across meta-analysis on the same outcome, or both. Some additional clarification would be welcome. 
```

```{asis}
While PRISMA is named along the review, it is not specifically indicated that it was followed. I would recommend that authors explicitely say it. 
```

```{asis}
Education outcomes: text indicates 12 effects from 8 reviews, but figure 2 only shows 11 effects from 7 reviews. A similar issue happens with Helath related outcomes: text indicates 17 effects, but I only see 15 in figure 3. What is going on?
```

```{asis}
“For example, a meta-analysis of the effect of television watching on learning among adolescents diagnosed with depression would be included.” This seems a strange choice, as it mixes very different populations. At the very least, the type of population should be indicated in table 1, and the impact of this discussed in the discussion.
```

>>>>

```{r setup-chunk, include = FALSE}
targets::tar_load(c(manuscript, manuscript_md))
options(revise_errors = FALSE)
manuscript <- suppressWarnings(
  revise::read_manuscript("reports/manuscript.md", PDF = TRUE)
)
get_revision <- function(id, ...) {
  suppressWarnings(revise::get_revision(id, ...))
}
```

@@

# Editor Comments
```{asis e1}
Reviewer 3 points out that your last search date is May 2020. We agree that this means the review is not as timely as it could be and ask that you update your search to September 2022, and redo your analyses with all newly included studies.
```

We have updated the search to September 2022.
We found a substantial amount of new literature had been published since our inital search, with an additional 108 meta-analyses included in the review.
While many of these were updates to existing reviews, we also included 110 new exposure/outcome combinations (or existing combinations for new age groups) that were not found in the original search.
We think that this increase in research demonstrates the level of interest in this area.

We'd also like to thank the editor and reviewers for their patience while we screened and extracted data from these additional reviews.

```{asis e2}
Reviewer 2's concerns about the appropriateness of your technical approach (notably: subjective characteristics of review selection, your statistical approach, and your choice to harmonize metrics of effect sizes) are significant and we ask that you prioritise addressing these issues when redoing your analyses.
```

@@

```{asis e3}
Both reviewers 2 and 3 are concerned about the lack of information on risk of bias assessment and population characteristics. Please ensure this information is clearly available and add data on both to Table 1.
```

@@

```{asis e4}
Reviewer 1 highlights the inappropriateness of causal language given that the majority of included studies speak to association, not causation. Please remove all inappropriate use of causal language accordingly.
```

Please see response to Reviewer 1, \Comment{r1_4}.

@@

```{asis r1_1}
As the authors note, “screen time” as a metric is highly criticized and problematic. This begs the question, though, of whether a wide-scale review of this sort, which retains a focus on screen time (although it also acknowledges other more nuanced metrics of exposure), is further perpetuating the issues seen by the broader field.
```

@@

`r get_revision("r1_1")`

```{asis r1_2}
The authors note that “no review has synthesized the evidence available across a broad range of outcome domains, such as physical health, education, physical and cognitive development, behaviours, and wellbeing.” The authors end up concluding that there are different magnitude and directions of associations for different outcomes and exposures (and, indeed, the mechanisms of these are highly different depending on the predictor-outcome combination), which makes me wonder whether casting such a wide net is helping the reader understand more or less about the research to date on technology use and child/adolescent outcomes? I would want to hear more justification in the manuscript itself on why they assert it is helpful to try and paint them with one broad brush?
```
\WorkInProgress
\todo{Suggestions welcome here}

@@

`r get_revision("r1_2")`

```{asis r1_3}
Page 10 notes that the study “examined the combinations of exposure and outcomes and removed any effects that appeared more than once, keeping the effect with the largest total sample size.” Did this take into consideration whether some meta-analyses of the same exposure-outcome pairs may have included mostly different studies (i.e., because they focused on different date ranges or some other inclusion criteria)?
```

@@

```{asis r1_4}
Causal language- The present study sought to “provide a holistic perspective on the influence of screens on children's lives across a broad range of outcomes,” but I am not convinced that the studies included in the meta-analyses are designed in ways that allow us to understand causal IMPACT at all. Many have criticized this literature for being largely self-reported (with flaws inherent to this method, which are reviewed in the present manuscript's discussion), observational, and cross-sectional, with very few rigorous experimental or well-controlled longitudinal designs that would enable researchers or the public to draw robust conclusions about the direction of associations. I fear that this comprehensive review, though rigorous, does not adequately attend to the fact that we do not usually know whether screens are causing helps or harms for youth, if different types of youth behaviors may be causing them to engage more with screens (e.g., sedentary youth may seek out more screen time; depressed youth may turn more to social media as an avoidance strategy), or if indeed there are third variables driving observed associations. Although the review here does a great job of summarizing the direction and strengths of associations across studies, I fear that it does not attend to these important issues in terms of how one ought to interpret them.
```

@@

`r get_revision("r1_4")`

@@

```{asis r1_5}
The manuscript notes that the nature of the data allowed for few age-based conclusions- I fear that this is a substantial limitation that deserves more discussion. It seems difficult to characterize all children's media use from age 0-18 in the same way, especially across such a wide range of developmental outcomes. A more nuanced treatment of developmental considerations would have been appreciated.
```

@@

```{asis r2_1}
I appreciate the opportunity to review this manuscript focusing on the impact of screen use on child well-being. This umbrella review organized findings from meta-analyses by child outcomes and screen types, converted pooled data into Pearson correlations as a unified estimate to facilitate cross-study comparisons, and reached a conclusion that general screen use and social media were associated with harmful impacts on child learning, literacy, body composition, and depression, and the potential risks could be mitigated by the content and context of screen use. This conclusion is somewhat similar to that of another umbrella review conducted by Stiglic and Viner in 2019 (PMID: 30606703). However, the current one made advances on including studies examining educational screen time and social media and harmonizing data from meta-analyses. 
```

@@

```{asis r2_2}
Abstract:

@@

```{asis r2_3}
Summary:
Page 4 line 59: the lack of comprehensive evidence hampers efforts to make an informed decision.
```

@@

```{asis r2_4}
Introduction:
Page 5 line 84-86: please further justify how a review study would make the limited evidence base less lacking or generate new findings.
```

@@

`r get_revision("r1_2")`

```{asis r2_5}
Page 5 line 87-90: I suggest improving the logic flow and citing more recent studies (2016 or newer) to highlight the potentially new additions of the current review. 
```

@@

```{asis r2_6}
Page 5 line 91-94: Please provide a more in-depth explanation on the advantages of a review study to include a broad spectrum of health outcomes. 
```

@@

```{asis r2_7}
Page 6 line 96-104: these guidelines provide age-staged recommendations and mainly target on recreational screen time. New evidence to support or reject these recommendations are important breakthroughs. So how does the current review contribute to the refinement of these guidelines? It could be proposed here to strengthen the justification of this study, and also need to be addressed in the discussion section. 
```

@@

```{asis r2_8}
Page 6 line 104-107: this is not a direct contrast. Longer screen time is needed to pose mental health risks, but short screen time can lead to other health issues. While guidelines are built on a comprehensive examination of health outcomes. Thus, I consider here as a weak argument/transition. The organization of the introduction section need to be improved. 
```

@@

```{asis r2_9}
Page 6 line 117-119: Stiglic and Viner's umbrella review summarized evidence across a broad range of outcome domains. Please further justify the current study in addition to theirs.
```

@@

```{asis r2_10}
Page 7 line 122: please define “any plausible outcomes” to make the scope more scientifically sound and robust. In addition, the result section included findings of behavioral outcomes (physical activity and sleep duration) which I was not considered as academic, health, and social-psychological outcomes. Thus, it is better to be clear about the types of outcomes at the beginning of the manuscript. 
```

We did not *a-priori* choose which outcomes would be included.
Instead, we chose to summarise the literature on for any meta-analysis where screen exposure was the independent variable.
We have removed the word "plausible", as we agree that makes the sentence unclear and the revised phrasing is more aligned with the eligibility critiera.
Our intention in the introduction is not to preempt the results, which means we do not outline the outcomes found in the introduction.

```{asis r2_11}
Page 7 line 123: the authors stated the application of “a broad approach”, while highlighted the importance of nuanced findings and guidelines. The introduction section would be improved by balancing these two important aspects. 
```

@@

```{asis r2_12}
Methods:
Page 8 line 146-148: the effects of screen use on youth with a clinical condition are likely be different from those of the general population. If this review included any, the population characteristics should be specified in the result section or in the figures. 
```

@@

```{asis r2_13}
Page 8 line 152: please define outcomes.
```

Per \comment{r2_10} above, we did not pre-specify outcomes and feel it would be inappropriate to revise our inclusion criteria.

```{asis r2_14}
Page 10 line 181-187: these two sections could be combined. 
```

@@

```{asis r2_15}
Page 10 line 190: Table 1 does not contain RoB info. 
```

@@

```{asis r2_16}
Page 10 line 195-196: the description of data conversion is not transparent. Pearson's r assumes linear relationship. But associations between screen use and well-being are often non-monotonic (Twenge 2020, PMID: 32303719). In addition, meta-analyses reporting odd ratios defined exposure outcomes in various ways. For example, Zhang et. al. 2016 compared the obesity risk by the lowest and highest TV viewing time, whereas Poorolajal et. al. 2020 compared watching TV > 1-2h/d with an unclear group. Can the harmonization of OR into R guarantee that the two values are comparable? Therefore, further justification is needed. 
```

@@

```{asis r2_17}
Page 10 Line 201-206: The inclusion/exclusion criteria are here and there (page 10 line 197-198, page 11 line 221-222, etc.). Please provide specific and full criteria of effect size inclusion/exclusion in one section.

@@

`r get_revision("r2_17")`

```{asis r2_18}
Page 11 line 222: Egger's test is not suitable for evaluating publication bias of ORs.
```

@@

```{asis r2_19}
Page 11 line 229-231: An effect with statistical credibility but showing P < .05 indicate no association of interest. 
```

@@

```{asis r2_20}
Page 12 line 232-233: “include systematic reviews without meta-analyses” conflicts “alongside the main meta-analytic findings”.
```

@@

```{asis r2_21}
Page 12 line 235: Harmonizing the metric of effect size does not guarantee the comparability of the strength of associations. Please fully justify the current practice with a thorough analysis of the pros and cons.
```

@@

```{asis r2_22}
Page 12 line 238-243: A significant P was not a criterion to consider studies as credible in other reviews. Not sure why it is a reason for altering the original plan. 
```

@@

```{asis r2_23}
Results
Page 12 line 247-248: please add a description that 66 studies contributed unique effect sizes to the current review. 
```

This information is available here (note that the updated search increased the number of reviews):

`r get_revision("r2_23")`

```{asis r2_24}
Figure 1: 1) what's the difference between references and studies in this figure? For those seven entries categorized as “non-studies”, what are they? 2) “other(explain)” is not self-explanatory. 3) what's the difference between non-target samples and wrong population? In addition, the total number in this box is 1848. 4) “larger study available”: I'm not confident about using sample size as a sole criterium of selecting studies. 
```

@@

```{asis r2_25}
Page 12 line 249-256: 1) I suggest adding a summary table (counts and percentages) of the basic characteristics of the included references/studies which including year range of publication, types of study designs, sample age categories, outcome types, and exposure types, quality assessment scores, etc. 2) The current description is quite confusing to me, for example, what does “cases” mean? How did you calculate up 197 cases? What appeared twice or more times, the combination of exposure/outcome by age group? 3) table 1: I suggest adding data of the original effect sizes. 
```

@@

```{asis r2_26}
Page 26 line 260-268, Information on quality assessment was provided in a supplementary file, not table 1. Please revise. 
```

@@

```{asis r2_27}
Page 27 line 291: Please provide pre-determined criteria of the magnitude of effects with supporting references. 
```

@@

```{asis r2_28}
Page 28 line 299-304: 119-31-30-43 = 15, not 17. 
```

Thank you for the attention to detail.
The reported numbers are now correct (note that they are different due to the updated search).

```{asis r2_29}
Three methodological issues needs to be clarified or justified. 
1. The selection of reviews to generate “unique” comparisons appeared to be subjective/unclear.
2. The statistical approach extensively reduced the evidence pool. For example, 46 unique effects on education outcomes was reduced to 12 and 119 unique effects on health outcomes was reduced to 17. 
3. Harmonizing the metrics of effect sizes into r may be invalid and placing the converted effect sizes in forest plot is somewhat deceiving. Because across-study comparisons are not guaranteed due to variations in study design, setups of exposure and outcome variables.
```

@@

1. (Not sure what to address)
2. xyz
3. We can understand the reviewer's concerns regarding the conversions of the effect sizes (although we disagree with the characterisation of our results as "somewhat deceiving").
We think it is worth considering the counter-factual to our approach: had we not converted effect sizes to a common metric, it would not be possible to make any comparisons between the effect sizes.

\todo{Add more to discussion about interpreting sizes carefully.}

```{asis r2_30}
Discussion
Page 31 line 362-368: I think these are important nuances. If the analytical plan was subjective altered in order to generate more consistent associations. Then, the practice can introduce selection bias. I suggest adding qualitative syntheses of those studies removed by not meeting the “statistical credibility” criteria. 
```

@@

```{asis r2_31}
Page 31 line 380-383: both guidelines mentioned recreational sedentary screen time. It is not in all instances. 
```

@@

```{asis r2_32}
Page 32 line 389-391: I assume that the data of primary studies was retrieved by the team whenever possible. But “failed to provide study-level data” make me wonder did not those reviews provide reference information of the included studies? 
```

There were two ways that the data from the primary studies could be included in our review:
* The data were provided in the paper (i.e., in forest plots, tables, or supplementary files); or
* The authors provided the data when contacted.

`r get_revision("r2_32")`

We did not retrive data from the primary studies when the data were not provided in the paper or by the author.
We did originally consider it, but the scope was such that it was not feasible.

```{asis r2_33}
Page 32 line 395: from my point of view, the evidence strength generated from data from ten loosely designed cross-sectional studies is weaker than 5 rigorously designed intervention studies or longitudinal studies. I wonder how the quality and quantity of studies were balanced in the current study.
```

\WorkInProgress
todo{include study design in the forest plots?}

@@

```{asis r3_1}
OVERALL IMPRESSION

@@

Thank you for the kind comments.
We are glad that you saw the value in our review.

```{asis r3_2}
MAJOR COMMENTS

We agree that our search was out of date.
We reran the search in September 2022, which revealed a substantial amount of new literature.

`r get_revision("r3_2")`

Our updated search did reveal some meta-analyses on screen use during or post-pandemic, but these tended to be small and it would be difficult to draw too many conclusions from these reviews.
The historic nature of reviews is an issue we acknowledge in our limitations:

`r get_revision("r3_2_2")`

```{asis r3_3}
Another main issue that I have with the article is that I feel that a better description of supplementary materials is needed. I have not been able to find a consistent description of the materials that can be found in them. Moreover, in the case of the CSV documents a variable dictionary would be most welcome. Somewhat relatedly, in line 190 (and 260) it says “see table 1”, so I was hoping to see some summary on the risk of bias evaluation in the table. I have not been able to find it there. In the Prisma checklist item 18 it says that risk of bias assessments can be found in OSF, but no mention of OSF is provided in the main text. After going through all the supplementary materials, I have been able to find the ratings in a file. My reading from all this is that the article has gone through several iterations and some systematizing and cleaning should be carried out to present in a more clear way the supplementary materials (an index of contents with a short description, table and figure captions, variable dictionary…)
```

@@

```{asis r3_4}
MINOR COMMENTS

@@

Our rationale for choosing the NHLBI was that we felt it could be applied equally to all fields than AMSTAR-2.
Reporting standards differ by discipline, and several of the items in AMSTAR-2 are typically only reported in medical fields.
While these should maybe be reported in all fields, we felt that the NHLBI was a more appropriate standard for our review.

```{asis r3_5}
The paragraph on age within the eligibility criteria is unclear to me: “(i.e., the highest individual study from the meta-analysis had a mean age was < 18 years).”: is it a mean age below eighteen (hence, potentially including some adults), or is it the oldest participant being under 18 (more clear-cut, but on the other hand limiting the number of outcomes)?
```

It is the former, which we have now clarified here:

`r get_revision("r3_5")`

We chose this as most reviews provided mean ages for individual studies but not age ranges, which meant we would not have been able to consistently apply the critiera.

```{asis r3_6}
“In this review we adopted a population-level perspective, meaning that we examined electronic media exposure that occurs during typical daily living activities (e.g., home, school-based electronic media exposure).”: I do not think this paragraph is fully clear. 
```

We agree that this was not clear, and have revised it:

`r get_revision("r3_6")`

```{asis r3_7}
“Outcomes: We included all reported outcomes.”: it might be worth adding “on benefits and risks”
```

We have updated this text.

`r get_revision("r3_7")`

```{asis r3_8}
Lines 200-204: it is unclear to me whether this refers to effects found within the same meta-analysis, across meta-analysis on the same outcome, or both. Some additional clarification would be welcome.

```

We agree this could have been clearer.
We have revised the text to indicate that it was both:

`r get_revision("r3_8")`

```{asis r3_9}
While PRISMA is named along the review, it is not specifically indicated that it was followed. I would recommend that authors explicitely say it. 
```

We have noted this under the *Methods* section.

```{asis r3_10}
Education outcomes: text indicates 12 effects from 8 reviews, but figure 2 only shows 11 effects from 7 reviews. A similar issue happens with Helath related outcomes: text indicates 17 effects, but I only see 15 in figure 3. What is going on?
```

Thank you for this attention to detail.
This is the same issue raised by Reviewer 2 (\comment{r2_28}), and we have corrected these numbers.

```{asis r3_11}
“For example, a meta-analysis of the effect of television watching on learning among adolescents diagnosed with depression would be included.” This seems a strange choice, as it mixes very different populations. At the very least, the type of population should be indicated in table 1, and the impact of this discussed in the discussion.
```
